### 2017-11-06 monograph/thesis/chapters/good_practices.tex
Created a motivation paragraph for motivation.tex' Code Beautifying

\end{englishtext}

>>>>

    \section{Semantic linefeed}

    \url{http://rhodesmill.org/brandon/2012/one-sentence-per-line/}
    \url{https://www.google.com.br/search?q=semantic+linefeeds}
    \url{https://news.ycombinator.com/item?id=4642395}
    \url{https://en.wikipedia.org/wiki/Wikipedia:Don%27t_use_line_breaks}
    \url{https://erambler.co.uk/blog/semantic-linefeeds/}
    \url{https://vi.stackexchange.com/questions/9828/insert-a-newline-after-punctuations}
    \url{https://blog.doismellburning.co.uk/semantic-linebreaks/}
    \url{https://scott.mn/2014/02/21/semantic_linewrapping/}
    \url{https://stackoverflow.com/questions/899114/when-you-write-tex-source-how-do-you-use-your-editors-word-wrap}

### 2017-11-06 monograph/thesis/chapters/motivation.tex
Created a motivation paragraph for motivation.tex' Code Beautifying

>>>>

    The problem about is,
    even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code formatter tool,
    which will be certainly limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.
